---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# indicators

<!-- badges: start -->
[![R-CMD-check](https://github.com/dataobservatory-eu/indicator/workflows/R-CMD-check/badge.svg)](https://github.com/dataobservatory-eu/indicator/actions)
[![Codecov test coverage](https://codecov.io/gh/dataobservatory-eu/indicator/branch/master/graph/badge.svg)](https://codecov.io/gh/dataobservatory-eu/indicator?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of indicators is to harvest data from various open data sources and form them into unique indicators of one of the automated data observatories on dataobservatory.eu:

- [economy.dataobservatory.eu](https://greendeal.dataobservatory.eu/)
- [greendeal.dataobservatory.eu](https://greendeal.dataobservatory.eu/)
- [music.dataobservatory.eu](https://music.dataobservatory.eu/)

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dataobservatory-eu/indicator")
```
## Create a mini database


See the vignettes:

```{r see-vignettes}
vignette( package="indicators")
```


Please note that the indicators project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.



