---
title: "Naming Conventions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Naming Conventions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(indicators)
```

## Indicator Table 
- `indicator_code`: Unique code for the indicator; the values are unique in *indicator_code*, *geo*, *time*, *value*, and *unit*.
- `unit`: measurement unit or currency code
- `geo`: geographical code of observation
- `time`: Time of observation, as Date
- `value`: Value of observation or indicator
- `year`: Year of observation
- `month`: Month of observation (often notional for annual indicators)
- `day`: Day of observation
- `frequency`: Frequency of observation, currently *A* as annual, *Q* as quarterly, *M* as monthly, *D* as daily, or unknown.
- `estimate`: See below.
- `db_source`: Database source code.

### Estimates

The `estimate` label describes the statistical technique used to impute missing values, or fix geographical coding.

- `actual`: The actual observation value at source, for example, by Eurostat.
- `missing`: Missing data, which is not filled by *locf*, *nocb*, *interpolate*, *forecast*, *backcast* or *impute*.
- `locf`: last observation carry forward
- `nocb`: next observation carry backward
- `interpolate`: interpolation in time between known values
- `forecast`: forecast with a given model.
- `backcast`: backcast with a given model.
- `impute`: An imputation technique was used that is not based on time series, but on a crossselection, or geographical, or other information. This is likely to be rather specific to the actual indicator.

The `recode` means that the regional codes needed to be fixed.

### Methods

The `method` label describes the statistical technique used to give the parameters oft the estimate, if the estimate is parametric. 


The `recode` means that the regional codes needed to be fixed.

## Metadata 

- `indicator_code`: the same as in value table.
- `title_at_source`: The name, title, or other human understandable description of the original source.
- `description_indicator`: A short textual description of the indicator. [A longer should be generated in html somewhere.]
- `db_source_code`: A unique source code that contains both *indicator_code* and *source* for easier programatic updating.
- `frequency`: Frequency of the indicator observations, currently *A*nnual, *Q*uarterly, *M*onthly, *D*aily, or unknown.
- `data_start`: The minimum value of *actual* observations. Further values may be backcasted.
- `data_end`: The last value of *actual* observations.  Further values may be forecasted.
- `last_update_data_source`: Last update at the data source. 
- `last_structure_change`: Last structural change at source.
- `last_update_data`: Last time the observatory updated the data, including various imputations, forecasts and backcasts.
- `actual`: The  number of actual observation values at source, for example, by Eurostat.
- `missing`: Number of missing data, which is not filled by *locf*, *nocb*, *interpolate*, *forecast*, *backcaskt* or *impute*.
- `locf`: number of *last observation carry forward* imputated values
- `nocb`: number of *next observation carry backward* imputated values
- `interpolate`: number of *interpolated* values
- `forecast`: number of values *forecasted* with a given model.
- `backcast`: number of values *backcasted* with a given model.
-`impute`: number of values filled with any other *imputation* method that is not based on time series, but cross-selectional, geographical or other information.
